Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-07-31 doc/ms.tex
Fix broken commas

Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshoruded in diffuse material following a binary merger or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (see e.g., \citealt{2014MNRAS.441..532D}). Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\;2013dy \citep{2013ApJ...778L..15Z} and SN\;2017cbv \citep{2017arXiv170608990H}.

>>>>

Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshoruded in diffuse material following a binary merger or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (see e.g., \citealt{2014MNRAS.441..532D}). Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv \citep{2017arXiv170608990H}.
